Awareness and Experience of Developers to\\ Outdated and License-violating Code on Stack Overflow:\\ An Online Survey

### 2017-11-07 cloverflow_technical_report/cloverflow_survey_rn.tex
Reverted the RN back to use violations

\title{Awareness and Experience of Developers to\\ Outdated and License-incompatible Code on Stack Overflow:\\ An Online Survey}
%\subtitle{Do you have a subtitle?\\ If so, write it here}

\titlerunning{SO Developers awareness: Outdated and License-incompatible Code}        % if too long for running head

@@

\begin{abstract}
We performed two online surveys of Stack Overflow answerers and visitors to
assess their awareness to outdated code and software licenses in Stack Overflow
answerers. The answerer survey targeted 607 highly reputed Stack Overflow users
and received a high response rate of 33\%. Our findings are as follows.
Although most of the code snippets in the answers are written from scratch,
there are code snippets cloned from the corresponding questions, from personal or company projects,
or from open source projects. Stack Overflow answerers are aware that some of
their snippets are outdated. However, 19\% of the participants report that they
rarely or never fix their outdated code. At least 98\% of the answerers never include
software licenses in their snippets and 69\% never check for licensing compatibility
with Stack Overflow's CC BY-SA 3.0 if they copy the code from other sources to
Stack Overflow answers. The visitor survey uses convenient sampling and received
89 responses. We found that 66\% of the participants experienced a problem from
cloning and reusing Stack Overflow snippets. Fifty-six percent of the visitors
never reported the problems back to the Stack Overflow post. Eighty-five percent of the
participants are not aware that StackOverflow applies the CC BY-SA 3.0 license, and sixty-two percent never
give attributions to Stack Overflow posts or answers they copied the code from.
Moreover, 66\% of the participants do not check for licensing compatibility between
the copied Stack Overflow code and their software. With these findings, we
suggest Stack Overflow raise awareness of their users, both answerers and
visitors, to the problem of outdated and license-incompatible code snippets.
\end{abstract}

@@

%This study is interested in the problem of outdated code and software licensing
%violations caused by code cloning on Internet-based question and answer
%websites.
Recent research shows that outdated third-party code and software licensing
incompatibility are ramifications by code cloning, i.e.~reusing source code by copying
and pasting. \cite{Xia2014} report that a large number of open source systems
reuse outdated third-party libraries from popular open source projects. Using
the outdated code give detrimental effects to the software since they may
introduce vulnerabilities. On the other hand, \cite{German2009} found that code
cloning leads to software license incompatibility among different systems.

@@

Asking and answering questions on Stack Overflow involves including source code
snippets, either in a question or an answer or both. While many answers contain
snippets that are written from scratch, there are several answers containing
code snippets copied from other sources. The copied snippets on Stack Overflow
are snapshots of the code at the time of copying. They are less frequently
updated than in normal software projects and might not be up-to-date with their
originals, which are further modified due to bug fixing or feature improvements.
Besides, some snippets are copied from software systems with stricter licenses
than Stack Overflow's Attribution-ShareAlike 3.0 Unported (CC BY-SA 3.0). Prior
to this study, we performed a quantitative empirical study using code clone
detection tools to locate cloned code snippets in accepted answers. We found
that many snippets were copied from open source projects. Some cloned snippets
are outdated (or obsolete) and some possibly incompatible with the original software
license. These snippets are potentially harmful to reuse. To accompany the
findings and gain insights into the cause of the problems, we resort to a
qualitative study using an online survey of Stack Overflow developers who 1)
regularly answer programming questions with code snippets and 2) reuse code
snippets from Stack Overflow. \textbf{The study aims to understand the
	developers' awareness and experience to outdated code and code licensing on
	Stack Overflow.}

@@

@@

\begin{enumerate}
	\item \textbf{RQ1 (Sources of Stack Overflow Answer Snippets):} \textit{Where are the code snippets in Stack Overflow answers from?}
	\item \textbf{RQ2 (Awareness of Stack Overflow answerers to outdated code):} \textit{Are Stack Overflow answerers aware of outdated code in their answers?}
	\item \textbf{RQ3 (Awareness of Stack Overflow answerers to licensing compatibility):} \textit{Are Stack Overflow answerers aware of software licensing
		incompatibility caused by code snippets in their answers?}
%	\item \textbf{RQ4 (Search for Coding Solutions):} \textit{Where do the developers search for programming solutions?}
	\item \textbf{RQ4 (Problems from Stack Overflow code snippets):} \textit{What are the problems Stack Overflow visitors experiencing from reusing code snippets on Stack Overflow?}
	\item \textbf{RQ5 (Software license of Stack Overflow code
            snippets):} \textit{Are Stack Overflow visitors aware of code licensing on Stack Overflow?}
\end{enumerate}

@@

\subsubsection*{RQ3: Are Stack Overflow answerers aware of software licensing
	incompatibility caused by code snippets in their answers?}

@@

We asked the answerers a follow-up question of how frequently they checked for compatibility between software license of the code snippets they copied to their
answers and Stack Overflow's CC BY-SA 3.0. As shown in
Figure~\ref{fig:survey_license_check}, 80 (69\%) and 58 (69\%) answerers from
group 1 and group 2 did not perform the checking. There are only approximately
10\% of the answerers who frequently checks for licensing compatibility when they
copy code snippets to Stack Overflow.

\vspace{0.5cm} \noindent\fbox{%
	\parbox[c][1.5cm]{0.98\textwidth}{%
		\textit{For RQ3, approximately 62\% of our participants are aware of CC BY-SA
			3.0 license enforced by Stack Overflow. However, 98--99\% of the answerers
			never include software license in their Stack Overflow snippets. Sixty-nine
			percent never check for licensing compatibility when they copy code snippets to
			Stack Overflow answers.} }%
} \vspace{0.5cm}

@@

Fifty seven participants (66\%) never check for licensing compatibility at all
when reusing Stack Overflow code (see
Figure~\ref{fig:survey_visitor_licensing_conflict_check}). Lastly, 9\% of
the participants experienced legal issues by reusing code snippets on Stack
Overflow (see Figure~\ref{fig:survey_visitor_legal_issue}). We did not
expect that any participant encountered legal issues as we are not
aware of such cases being reported in the literature. It would
be interesting to followup on the kind of legal issues that have been
encountered, however, as we designed the
survey to be anonymous, it was not possible to contact the participants for further details.

@@

\begin{figure} \centering
	\includegraphics[width=.4\linewidth]{survey_visitor_licensing_conflict_check} 
	\caption{Checking for licensing compatibility from reusing Stack Overflow snippets}
	\label{fig:survey_visitor_licensing_conflict_check} 
\end{figure}

@@

\vspace{0.5cm} \noindent\fbox{%
	\parbox[c][1.7cm]{0.98\textwidth}{%
		\textit{For RQ5, 85\% of the participants are not aware of Stack Overflow CC
			BY-SA 3.0 license and 62\% never give attributions to the Stack Overflow posts
			they copied the code snippets from. We found that 66\% of the visitors never check for software
	licensing compatibility between Stack Overflow code snippets and their projects.
	9\% of the participants encountered legal issues.}}%
} \vspace{0.5cm}

@@

Regarding software license, the responses from the two groups agree with each
other. The answerers in both groups show the same level of awareness to Stack
Overflow CC BY-SA 3.0 license (62.1\% and 62.3\%). Similarly, the answerers in
both groups neither include software license in their code snippets (98\% and
99\%) nor check of license compatibility between their code snippet's and Stack
Overflow CC BY-SA 3.0 (69\%).

@@

We present the results from online surveys of Stack Overflow answerers and
visitors regarding their awareness and experience of answering and reusing code
snippets on Stack Overflow. We are particularly interested in cloned code
snippets in Stack Overflow answers. Thus, the two online surveys are performed to
find out the \textit{origin} of code snippets in Stack Overflow answers and
\textit{awareness} of Stack Overflow developers, both answerers and visitors,
to the problem of outdated and license-incompatible code.

@@

Approximately 60\% of the answerers are aware that Stack Overflow
applies the CC BY-SA 3.0
license to code on Stack Overflow. Ninety-eight to ninety-nine percent
do not include a license in their answers nor check for licensing compatibility when
they copy the code from another location to their answer. Some developers
believe the code is too small and fall under fair use policy. Many answerers
mention the license of their code in their profile page instead.

@@

Eighty-five percent of the visitors are not aware of Stack Overflow's CC BY-SA
3.0 and sixty-two percent never give attributions to Stack Overflow posts that they copied
the code from. Moreover, sixty-six percent never check for licensing compatibility while
reusing Stack Overflow code snippets in their software
projects. Unexpectedly, 9\%
of the participants encountered legal issues.

With these findings, we
suggest Stack Overflow raise an awareness of their users, both the answerers and
the visitors, to the problem of outdated and license-incompatible code snippets.

>>>>

\title{Awareness and Experience of Developers to\\ Outdated and License-violating Code on Stack Overflow:\\ An Online Survey}
%\subtitle{Do you have a subtitle?\\ If so, write it here}

\titlerunning{SO Developers awareness: Outdated and License-violating Code}        % if too long for running head

@@

\begin{abstract}
We performed two online surveys of Stack Overflow answerers and visitors to
assess their awareness to outdated code and software licenses in Stack Overflow
answerers. The answerer survey targeted 607 highly reputed Stack Overflow users
and received a high response rate of 33\%. Our findings are as follows.
Although most of the code snippets in the answers are written from scratch,
there are code snippets cloned from the corresponding questions, from personal or company projects,
or from open source projects. Stack Overflow answerers are aware that some of
their snippets are outdated. However, 19\% of the participants report that they
rarely or never fix their outdated code. At least 98\% of the answerers never include
software licenses in their snippets and 69\% never check for licensing conflicts
with Stack Overflow's CC BY-SA 3.0 if they copy the code from other sources to
Stack Overflow answers. The visitor survey uses convenient sampling and received
89 responses. We found that 66\% of the participants experienced a problem from
cloning and reusing Stack Overflow snippets. Fifty-six percent of the visitors
never reported the problems back to the Stack Overflow post. Eighty-five percent of the
participants are not aware that StackOverflow applies the CC BY-SA 3.0 license, and sixty-two percent never
give attributions to Stack Overflow posts or answers they copied the code from.
Moreover, 66\% of the participants do not check for licensing conflicts between
the copied Stack Overflow code and their software. With these findings, we
suggest Stack Overflow raise awareness of their users, both answerers and
visitors, to the problem of outdated and license-violating code snippets.
\end{abstract}

@@

%This study is interested in the problem of outdated code and software licensing
%violations caused by code cloning on Internet-based question and answer
%websites.
Recent research shows that outdated third-party code and software licensing
conflicts are ramifications by code cloning, i.e.~reusing source code by copying
and pasting. \cite{Xia2014} report that a large number of open source systems
reuse outdated third-party libraries from popular open source projects. Using
the outdated code give detrimental effects to the software since they may
introduce vulnerabilities. On the other hand, \cite{German2009} found that code
cloning leads to software license conflicts among different systems.

@@

Asking and answering questions on Stack Overflow involves including source code
snippets, either in a question or an answer or both. While many answers contain
snippets that are written from scratch, there are several answers containing
code snippets copied from other sources. The copied snippets on Stack Overflow
are snapshots of the code at the time of copying. They are less frequently
updated than in normal software projects and might not be up-to-date with their
originals, which are further modified due to bug fixing or feature improvements.
Besides, some snippets are copied from software systems with stricter licenses
than Stack Overflow's Attribution-ShareAlike 3.0 Unported (CC BY-SA 3.0). Prior
to this study, we performed a quantitative empirical study using code clone
detection tools to locate cloned code snippets in accepted answers. We found
that many snippets were copied from open source projects. Some cloned snippets
are outdated (or obsolete) and some possibly violate the original software
license. These snippets are potentially harmful to reuse. To accompany the
findings and gain insights into the cause of the problems, we resort to a
qualitative study using an online survey of Stack Overflow developers who 1)
regularly answer programming questions with code snippets and 2) reuse code
snippets from Stack Overflow. \textbf{The study aims to understand the
	developers' awareness and experience to outdated code and code licensing on
	Stack Overflow.}

@@

We use the term ``license-violating code snippets'' or ``code with licensing conflicts''
interchangeably to refer to Stack Overflow cloned code snippets that \textit{potentially} violate the
original license by not including the original license statement in the cloned snippets and
adopt the Stack Overflow CC BY-SA 3.0 license instead.

@@

\begin{enumerate}
	\item \textbf{RQ1 (Sources of Stack Overflow Answer Snippets):} \textit{Where are the code snippets in Stack Overflow answers from?}
	\item \textbf{RQ2 (Awareness of Stack Overflow answerers to outdated code):} \textit{Are Stack Overflow answerers aware of outdated code in their answers?}
	\item \textbf{RQ3 (Awareness of Stack Overflow answerers to licensing violations):} \textit{Are Stack Overflow answerers aware of software licensing
		violations caused by code snippets in their answers?}
%	\item \textbf{RQ4 (Search for Coding Solutions):} \textit{Where do the developers search for programming solutions?}
	\item \textbf{RQ4 (Problems from Stack Overflow code snippets):} \textit{What are the problems Stack Overflow visitors experiencing from reusing code snippets on Stack Overflow?}
	\item \textbf{RQ5 (Software license of Stack Overflow code
            snippets):} \textit{Are Stack Overflow visitors aware of code licensing on Stack Overflow?}
\end{enumerate}

@@

\subsubsection*{RQ3: Are Stack Overflow answerers aware of software licensing
	violations caused by code snippets in their answers?}

@@

We asked the answerers a follow-up question of how frequently they checked for
conflicts between software license of the code snippets they copied to their
answers and Stack Overflow's CC BY-SA 3.0. As shown in
Figure~\ref{fig:survey_license_check}, 80 (69\%) and 58 (69\%) answerers from
group 1 and group 2 did not perform the checking. There are only approximately
10\% of the answerers who frequently checks for licensing conflicts when they
copy code snippets to Stack Overflow.

\vspace{0.5cm} \noindent\fbox{%
	\parbox[c][1.5cm]{0.98\textwidth}{%
		\textit{For RQ3, approximately 62\% of our participants are aware of CC BY-SA
			3.0 license enforced by Stack Overflow. However, 98--99\% of the answerers
			never include software license in their Stack Overflow snippets. Sixty-nine
			percent never check for licensing conflicts when they copy code snippets to
			Stack Overflow answers.} }%
} \vspace{0.5cm}

@@

Fifty seven participants (66\%) never check for licensing conflicts at all
when reusing Stack Overflow code (see
Figure~\ref{fig:survey_visitor_licensing_conflict_check}). Lastly, 9\% of
the participants experienced legal issues by reusing code snippets on Stack
Overflow (see Figure~\ref{fig:survey_visitor_legal_issue}). We did not
expect that any participant encountered legal issues as we are not
aware of such cases being reported in the literature. It would
be interesting to followup on the kind of legal issues that have been
encountered, however, as we designed the
survey to be anonymous, it was not possible to contact the participants for further details.

@@

\begin{figure} \centering
	\includegraphics[width=.4\linewidth]{survey_visitor_licensing_conflict_check} 
	\caption{Checking for licensing conflicts from reusing Stack Overflow snippets}
	\label{fig:survey_visitor_licensing_conflict_check} 
\end{figure}

@@

\vspace{0.5cm} \noindent\fbox{%
	\parbox[c][1.7cm]{0.98\textwidth}{%
		\textit{For RQ5, 85\% of the participants are not aware of Stack Overflow CC
			BY-SA 3.0 license and 62\% never give attributions to the Stack Overflow posts
			they copied the code snippets from. We found that 66\% of the visitors never check for software
	licensing conflicts between Stack Overflow code snippets and their projects.
	9\% of the participants encountered legal issues.}}%
} \vspace{0.5cm}

@@

Regarding software license, the responses from the two groups agree with each
other. The answerers in both groups show the same level of awareness to Stack
Overflow CC BY-SA 3.0 license (62.1\% and 62.3\%). Similarly, the answerers in
both groups neither include software license in their code snippets (98\% and
99\%) nor check of licensing conflicts between their code snippet's and Stack
Overflow CC BY-SA 3.0 (69\%).

@@

We present the results from online surveys of Stack Overflow answerers and
visitors regarding their awareness and experience of answering and reusing code
snippets on Stack Overflow. We are particularly interested in cloned code
snippets in Stack Overflow answers. Thus, the two online surveys are performed to
find out the \textit{origin} of code snippets in Stack Overflow answers and
\textit{awareness} of Stack Overflow developers, both answerers and visitors,
to the problem of outdated and license-violating code.

@@

Approximately 60\% of the answerers are aware that Stack Overflow
applies the CC BY-SA 3.0
license to code on Stack Overflow. Ninety-eight to ninety-nine percent
do not include a license in their answers nor check for licensing conflicts when
they copy the code from another location to their answer. Some developers
believe the code is too small and fall under fair use policy. Many answerers
mention the license of their code in their profile page instead.

@@

Eighty-five percent of the visitors are not aware of Stack Overflow's CC BY-SA
3.0 and sixty-two percent never give attributions to Stack Overflow posts that they copied
the code from. Moreover, sixty-six percent never check for licensing conflicts while
reusing Stack Overflow code snippets in their software
projects. Unexpectedly, 9\%
of the participants encountered legal issues.

With these findings, we
suggest Stack Overflow raise an awareness of their users, both the answerers and
the visitors, to the problem of outdated and license-violating code snippets.
